---
title: "Untitled"
author: "Yutong Lu"
date: "`r Sys.Date()`"
output: html_document
---

# Packages and working directory
```{r}
library(tidyverse)
library(arm)
library(ltmle)
library(ipw) #MSM;
library(gfoRmula) #g-computation;

#This sets the working directory to the current location of the RMD file
path <- rstudioapi::getActiveDocumentContext()$path
Encoding(path) <- "UTF-8"
setwd(dirname(path))
```

# Scenario 4

- 1000 patients and 3 visits
- y, an end-of-study binary outcome;
- z, a binary treatment assignment;
- w1 and w2 are two baseline covariates (one continuous, one binary) i.e., age, sex;
- L1 and L2 are two time-dependent covariates (one continuous, one binary);
- censoring = right censoring
- Interaction = interaction treatment effect on the outcome;
- linearity = additive linear effect for the outcome model;

```{r}
set.seed(123)
ntot=1000; #500 or 200 as small sample example;
samplesize=10000
```

# Visit 1

```{r}
# covariates
w1 <- rbinom(ntot, 1, prob = 0.5) #50-50 male and female (reference);
w2 <- rnorm(ntot, mean = 12, sd = 4) #age;
L1_1 <- rbinom(ntot, 1, prob = plogis(-1 + 0.01*w1 + 0.01*w2)) #a age & sex related baseline binary clinical variable;
L2_1 <- rnorm(ntot, mean = (0.01*w1 + 0.01*w2), sd = 1) #a age & sex related baseline continuous clinical variable;

# Exposure;
a_1 <- rbinom(ntot, 1, plogis(-1 - 0.01*w1 + 0.01*w2 - 0.1*L1_1 + 0.1*L2_1))
table(a_1)
```

# Visit 2

```{r}
L1_2 <- rbinom(ntot, 1, plogis(-1 + 0.01*w1 + 0.01*w2 + 0.2*L1_1 - 0.2*a_1))
L2_2 <- rnorm(ntot, mean = (L2_1 - 0.01*w1 + 0.01*w2 - 0.2*a_1), sd = 1)
a_2 <- rbinom(ntot, 1, plogis(-1 - 0.01*w1 + 0.01*w2 - 0.1*L1_2 + 0.1*L2_2 + a_1))
table(a_1, a_2)
```

# Visit 3

```{r}
# disease activity score, continuous;
# a_1 and a_2 are dominant predictors for y, approximately 1 unit increase in a_1 result in 1 unit change on y
# but confounders have smaller effect in this setting, 1 unit increase in w2, y is only changed on average by 0.1;
y <- rnorm(ntot, mean = (1 - 1*a_1 - 2*a_2 + 0.01*a_1*a_2 - 0.2*w1 + 0.1*w2 + 0.4*L1_2 + 0.2*L2_2) , sd = 1)
mean(y)
```

# Censoring

```{r}
# simulate c from a binary + logistic format;
# use 'plogis' function to calculate exp(x)/(1 + exp(x))
# x is log-odds

to_prob <- function(x){
  x <- exp(x)
  x <- x/(x+1)
  return(x)
}

c_1 <- rbinom(ntot, 1, 
              prob=to_prob(-3 + 0.002*w1 + 0.001*w2))
c_2 <- rbinom(ntot, 1,
              prob = to_prob(-3 + 0.002*w1 + 0.001*w2 + 0.003*L1_1 + 0.005*L2_1 + 
                               0.01*a_1))

id <- rep(1:1000)
dat4 <- data.frame(id, w1, w2, c_1, L1_1, L2_1, a_1, c_2, L1_2, L2_2, a_2, y)
dat4 <- dat4 %>% 
  mutate(cum_a = a_1 + a_2,
         c = case_when(c_1 == 1 | c_2 == 1 ~ 1,
                       TRUE ~ 0)) %>% 
  select(id, cum_a, c, everything())

sum(dat4$c)/1000

dat4$L1_1[dat4$c_1==1] <- NA
dat4$L2_1[dat4$c_1==1] <- NA
dat4$a_1[dat4$c_1==1] <- NA

dat4$L1_2[dat4$c_2==1] <- NA
dat4$L2_2[dat4$c_2==1] <- NA
dat4$a_2[dat4$c_2==1] <- NA
dat4$y[dat4$c_2==1] <- NA

# dat4$c[dat4$c==0] <- "uncensored"
# dat4$c[dat4$c==1] <- "censored"
dat4$c <- as.factor(dat4$c)
```

# True distribution

```{r}
mytrue <- function(a_1s = 1, a_2s = 1){
  #visit 1;
  w1sim <- rbinom(samplesize, 1, prob = 0.5) #50-50 male and female;
  w2sim <- rnorm(samplesize, mean = 12, sd = 4) #age;
  L1_1sim <- rbinom(samplesize, 1, prob = plogis(-1 + 0.01*w1sim + 0.01*w2sim)) #a age related baseline binary clinical variable;
  L2_1sim <- rnorm(samplesize, mean = (0.01*w1sim + 0.01*w2sim), sd = 1) #a age & sex related baseline continuous clinical variable;
  
  #Visit 2, simulate all potential variables;
  L1_2sim <- rbinom(samplesize, 1, plogis(-1 + 0.01*w1sim + 0.01*w2sim + 0.2*L1_1sim - 0.2*a_1s))
  L2_2sim <- rnorm(samplesize, mean = (L2_1sim - 0.01*w1sim + 0.01*w2sim - 0.2*a_1s), sd = 1)
  
  #Visit 3, simulate potential outcomes;
  truemean = (1 - 1*a_1s - 2*a_2s + 0.01*a_1s*a_2s - 0.1*w1sim + 0.01*w2sim + 0.1*L1_2sim + 0.1*L2_2sim)
  return(mean(truemean))
}

mytrue(a_1s = 1, a_2s = 1) #potential outcome Y(a_1=1, a_2=1);
mytrue(a_1s = 0, a_2s = 0)
mytrue(a_1s = 1, a_2s = 0)
mytrue(a_1s = 0, a_2s = 1)
mytrue(a_1s = 1, a_2s = 1) - mytrue(a_1s = 0, a_2s = 0); #-3.010579, this can change due to random sampling;
```

# convert one row per subject to two rows

```{r}
dat4_new <- dat4 %>%
  pivot_longer(cols = -c(w1,w2,y,c, cum_a, id,c_1,c_2), 
               names_to = c("variable","visit"), 
               names_sep = "_", 
               values_to = "value") %>% 
  pivot_wider(names_from = variable, values_from = value) %>% 
  mutate(time = case_when(visit == 1 ~ 0,
                          visit == 2 ~ 1))

dat4_new$y[dat4_new$visit == 1] <- NA

dat4_new$visit <- as.numeric(dat4_new$visit)
dat4_new$w1 <- as.numeric(dat4_new$w1)

dat4_new$cum_a[dat2_new$time == 0] <- dat2$a_1
dat4_new$cum_a[dat2_new$time == 1] <- dat2$a_1+dat2$a_2
```

# Saving as CSV
```{r}
write_csv(dat4,
          file = "datasets/scenario_4_wide_dataset.csv")
write_csv(dat4_new,
          file = "datasets/scenario_4_long_dataset.csv")
```

# End






