---
title: "scenario2_dataset_simulation"
author: "Yutong Lu"
date: "`r Sys.Date()`"
output: html_document
---

Creating the simulated dataset for scenario 2

Kuan: updated on June 23, 2022.

# Packages and working directory
```{r}
library(tidyverse)
library(arm)
library(survey)
library(ltmle)
library(ipw) #MSM;
library(gfoRmula) #g-computation;
library(gtsummary)

#This sets the working directory to the current location of the RMD file
path <- rstudioapi::getActiveDocumentContext()$path
Encoding(path) <- "UTF-8"
setwd(dirname(path))

#pre-define function;
expit <- function(x){
  x <- exp(x)/(exp(x)+1) 
  return(x)
}
```

# Scenario 2

- 1000 patients and 3 visits
- y, an end-of-study binary outcome;
- z, a binary treatment assignment;
- w1 and w2 are two baseline covariates (one continuous, one binary) i.e., age, sex;
- L1 and L2 are two time-dependent covariates (one continuous, one binary);
- censoring = no censoring
- Interaction = interaction treatment effect on the outcome;
- linearity = additive linear effect for the outcome model;

# Visit 1

```{r}
set.seed(123)
ntot=1000;
samplesize=10000
# covariates;
w1 <- rbinom(ntot, 1, prob = 0.5) #50-50 male and female (reference);
w2 <- rnorm(ntot, mean = 12, sd = 4) #age;
L1_1 <- rbinom(ntot, 1, prob = expit(-1 + 0.01*w1 + 0.01*w2)) #a age & sex related baseline binary clinical variable;
L2_1 <- rnorm(ntot, mean = (0.01*w1 + 0.01*w2), sd = 1) #a age & sex related baseline continuous clinical variable;

# Exposure;
a_1 <- rbinom(ntot, 1, expit(-1 - 0.01*w1 + 0.01*w2 - 0.1*L1_1 + 0.1*L2_1))
# table(a_1)
```

# Visit 2

```{r}
# observational data;
L1_2 <- rbinom(ntot, 1, expit(-1 + 0.01*w1 + 0.01*w2 + 0.2*L1_1 - 0.2*a_1))
L2_2 <- rnorm(ntot, mean = (L2_1 - 0.01*w1 + 0.01*w2 - 0.2*a_1), sd = 1)
a_2 <- rbinom(ntot, 1, expit(-1 - 0.01*w1 + 0.01*w2 - 0.1*L1_2 + 0.1*L2_2 + a_1))
# table(a_1, a_2)

# potential variables at visit 2 given treatment;
L1_2_0 <- rbinom(ntot, 1, expit(-1 + 0.01*w1 + 0.01*w2 + 0.2*L1_1))
L1_2_1 <- rbinom(ntot, 1, expit(-1 + 0.01*w1 + 0.01*w2 + 0.2*L1_1- 0.2))
L2_2_0 <- rnorm(ntot, mean = (L2_1 - 0.01*w1 + 0.01*w2), sd = 1)
L2_2_1 <- rnorm(ntot, mean = (L2_1 - 0.01*w1 + 0.01*w2 - 0.2), sd = 1)
a_2_0 <- rbinom(ntot, 1, expit(-1 - 0.01*w1 + 0.01*w2 - 0.1*L1_2_0 + 0.1*L2_2_0))
a_2_1 <- rbinom(ntot, 1, expit(-1 - 0.01*w1 + 0.01*w2 - 0.1*L1_2_1 + 0.1*L2_2_1 + 1))
```

# Visit 3

```{r}
# disease activity score, continuous;
# a_1 and a_2 are dominant predictors for y, approximately 1 unit increase in a_1 result in 1 unit change on y
# but confounders have smaller effect in this setting, 1 unit increase in w2, y is only changed on average by 0.1;

y <- rbinom(ntot, 1, prob = expit(- 1 + log(0.9)*a_1 + log(0.85)*a_2 + log(1.01)*a_1*a_2 
                            - 0.2*w1 + 0.1*w2 + 0.4*L1_2 + 0.2*L2_2))

# look at simulating binary from odds ratios, different ways to do it
table(y);
sum(y)/ntot; #proportional of patients with a positive binary outcome (1);

# saving final data;
id <- rep(1:1000)
dat2 <- data.frame(id, cum_a = a_1 + a_2, w1, w2, L1_1, L2_1, a_1, L1_2, L2_2, a_2, y)

# potential outcomes and the true simulated causal contrast;
prob_00 <- expit(- 1 - 0.2*w1 + 0.1*w2 + 0.4*L1_2_0 + 0.2*L2_2_0)
prob_10 <- expit(- 1 + log(0.9) - 0.2*w1 + 0.1*w2 + 0.4*L1_2_1 + 0.2*L2_2_1)
prob_01 <- expit(- 1 + log(0.85) - 0.2*w1 + 0.1*w2 + 0.4*L1_2_0 + 0.2*L2_2_0)
prob_11 <- expit(- 1 + log(0.9) + log(0.85) + log(1.01) - 0.2*w1 + 0.1*w2 + 0.4*L1_2_1 + 0.2*L2_2_1)

# True absolute risk difference, -0.07372847;
mean(prob_11) - mean(prob_00)
# True risk ratio, 0.8695818;
mean(prob_11)/mean(prob_00)
# True odds ratio, 0.7268491;
mean(prob_11/(1-prob_11))/mean(prob_00/(1-prob_00))

mytrue <- function(a_1s = 1, a_2s = 1){
  #visit 1;
  w1sim <- rbinom(samplesize, 1, prob = 0.5) #50-50 male and female;
  w2sim <- rnorm(samplesize, mean = 12, sd = 4) #age;
  L1_1sim <- rbinom(samplesize, 1, prob = plogis(-1 + 0.01*w1sim + 0.01*w2sim)) #a age related baseline binary clinical variable;
  L2_1sim <- rnorm(samplesize, mean = (0.01*w1sim + 0.01*w2sim), sd = 1) #a age & sex related baseline continuous clinical variable;
  
  #Visit 2, simulate all potential variables;
  L1_2sim <- rbinom(samplesize, 1, plogis(-1 + 0.01*w1sim + 0.01*w2sim + 0.2*L1_1sim - 0.2*a_1s))
  L2_2sim <- rnorm(samplesize, mean = (L2_1sim - 0.01*w1sim + 0.01*w2sim - 0.2*a_1s), sd = 1)
  
  #Visit 3, simulate potential outcomes;
  # calc odds of y=1
  truemean = expit(- 1 + log(0.9)*a_1s + log(0.85)*a_2s + log(1.01)*a_1s*a_2s 
                     - 0.2*w1sim + 0.1*w2sim + 0.4*L1_2sim + 0.2*L2_2sim)
  return(mean(truemean))
}
# convert prob into odds
# N0TE: plogis and expit are very close but not exactly the same
mytrue(a_1s = 1, a_2s = 1) #potential outcome Y(a_1=1, a_2=1);
mytrue(a_1s = 0, a_2s = 0)
mytrue(a_1s = 1, a_2s = 0)
mytrue(a_1s = 0, a_2s = 1)
mytrue(a_1s = 1, a_2s = 1) - mytrue(a_1s = 0, a_2s = 0) #-0.07133047, risk difference;
mytrue(a_1s = 1, a_2s = 1)/mytrue(a_1s = 0, a_2s = 0) # Risk Ratio, 0.8699124;
(mytrue(a_1s = 1, a_2s = 1)/(1-mytrue(a_1s = 1, a_2s = 1)))/(mytrue(a_1s = 0, a_2s = 0)/(1-mytrue(a_1s = 0, a_2s = 0))) #0.7411494, Odds Ratio



```

# Creating long dataset
```{r}
dat2_new <- dat2 %>%
  pivot_longer(cols = -c(w1,w2,y,id,cum_a), 
               names_to = c("variable","visit"), 
               names_sep = "_", 
               values_to = "value") %>% 
  pivot_wider(names_from = variable, values_from = value) %>% 
  mutate(time = case_when(visit == 1 ~ 0,
                          visit == 2 ~ 1))

dat2_new$y[dat2_new$visit == 1] <- NA

dat2_new$visit <- as.numeric(dat2_new$visit)
dat2_new$w1 <- as.numeric(dat2_new$w1)

dat2_new$cum_a[dat2_new$time == 0] <- dat2$a_1
dat2_new$cum_a[dat2_new$time == 1] <- dat2$a_1+dat2$a_2
```

# Saving as CSV
```{r}
write_csv(dat2,
          file = "datasets/scenario_2_wide_dataset.csv")
write_csv(dat2_new,
          file = "datasets/scenario_2_long_dataset.csv")
```

# End
