---
title: "Untitled"
author: "Yutong Lu"
date: "`r Sys.Date()`"
output: html_document
---

Creating the simulated dataset for scenario 3

# Packages and working directory
```{r}
library(tidyverse)
library(arm)
library(ltmle)
library(ipw) #MSM;
library(gfoRmula) #g-computation;

#This sets the working directory to the current location of the RMD file
path <- rstudioapi::getActiveDocumentContext()$path
Encoding(path) <- "UTF-8"
setwd(dirname(path))
```

# Scenario 3

- 1000 patients and 3 visits
- y, an end-of-study binary outcome;
- z, a binary treatment assignment;
- w1 and w2 are two baseline covariates (one continuous, one binary) i.e., age, sex;
- L1 and L2 are two time-dependent covariates (one continuous, one binary);
- censoring = no censoring
- Interaction = interaction treatment effect on the outcome;
- linearity = non-linear effect for the outcome model

```{r}
set.seed(123)
ntot=1000;
samplesize=10000
```

# Visit 1
```{r}
# visit 1;
# covariates;
w1 <- rbinom(ntot, 1, prob = 0.5) #50-50 male and female (reference);
w2 <- rnorm(ntot, mean = 12, sd = 4) #age;
L1_1 <- rbinom(ntot, 1, prob = plogis(-1 + 0.01*w1 + 0.01*w2)) #a age & sex related baseline binary clinical variable;
L2_1 <- rnorm(ntot, mean = (0.01*w1 + 0.01*w2), sd = 1) #a age & sex related baseline continuous clinical variable;

# Exposure;
a_1 <- rbinom(ntot, 1, plogis(-1 - 0.01*w1 + 0.01*w2 - 0.1*L1_1 + 0.1*L2_1))
table(a_1)
```

# Visit 2
```{r}
L1_2 <- rbinom(ntot, 1, plogis(-1 + 0.01*w1 + 0.01*w2 + 0.2*L1_1 - 0.2*a_1))
L2_2 <- rnorm(ntot, mean = (L2_1 - 0.01*w1 + 0.01*w2 - 0.2*a_1), sd = 1)
a_2 <- rbinom(ntot, 1, plogis(-1 - 0.01*w1 + 0.01*w2 - 0.1*L1_2 + 0.1*L2_2 + a_1))
table(a_1, a_2)
```

# Visit 3
```{r}
y <- rnorm(ntot, mean = (1 - 1*a_1 - 2*a_2 + 0.01*a_1*a_2 - 0.2*w1 + 0.1*w2 + 0.4*L1_2 + 0.2*L2_2 + 
                           exp(L1_2) + 0.02*L2_2^3) , sd = 1)
mean(y);

id <- rep(1:1000)
dat3 <- data.frame(id, w1, w2, L1_1, L2_1, a_1, L1_2, L2_2, a_2, y)
dat3 <- dat3 %>% mutate(cum_a = a_1 + a_2) %>% select(id, cum_a, everything())

mytrue <- function(a_1s = 1, a_2s = 1){
  #visit 1;
  w1sim <- rbinom(samplesize, 1, prob = 0.5) #50-50 male and female;
  w2sim <- rnorm(samplesize, mean = 12, sd = 4) #age;
  L1_1sim <- rbinom(samplesize, 1, prob = plogis(-1 + 0.01*w1sim + 0.01*w2sim)) #a age related baseline binary clinical variable;
  L2_1sim <- rnorm(samplesize, mean = (0.01*w1sim + 0.01*w2sim), sd = 1) #a age & sex related baseline continuous clinical variable;
  
  #Visit 2, simulate all potential variables;
  L1_2sim <- rbinom(samplesize, 1, plogis(-1 + 0.01*w1sim + 0.01*w2sim + 0.2*L1_1sim - 0.2*a_1s))
  L2_2sim <- rnorm(samplesize, mean = (L2_1sim - 0.01*w1sim + 0.01*w2sim - 0.2*a_1s), sd = 1)
  
  #Visit 3, simulate potential outcomes;
  truemean = (1 - 1*a_1s - 2*a_2s + 0.01*a_1s*a_2s - 0.2*w1sim + 0.1*w2sim + 0.4*L1_2sim + 0.2*L2_2sim + 
                exp(L1_2sim) + 0.02*L2_2sim^3)
  return(mean(truemean))
}

mytrue(a_1s = 1, a_2s = 1) #potential outcome Y(a_1=1, a_2=1);
mytrue(a_1s = 0, a_2s = 0)
mytrue(a_1s = 1, a_2s = 0)
mytrue(a_1s = 0, a_2s = 1)
mytrue(a_1s = 1, a_2s = 1) - mytrue(a_1s = 0, a_2s = 0)
```

# Creating long dataset
```{r}
dat3_new <- dat3 %>%
  pivot_longer(cols = -c(w1,w2,y,id,cum_a), 
               names_to = c("variable","visit"), 
               names_sep = "_", 
               values_to = "value") %>% 
  pivot_wider(names_from = variable, values_from = value) %>% 
  mutate(time = case_when(visit == 1 ~ 0,
                          visit == 2 ~ 1))

dat3_new$y[dat3_new$visit == 1] <- NA

dat3_new$visit <- as.numeric(dat3_new$visit)
dat3_new$w1 <- as.numeric(dat3_new$w1)

dat3_new$cum_a[dat3_new$time == 0] <- dat3$a_1
dat3_new$cum_a[dat3_new$time == 1] <- dat3$a_1+dat3$a_2
```

# Saving as CSV
```{r}
write_csv(dat3,
          file = "datasets/scenario_3_wide_dataset.csv")
write_csv(dat3_new,
          file = "datasets/scenario_3_long_dataset.csv")
```

# End


