---
title: "BMSM simulator - x11 remains constant"
author: "Ismail Benchekroun"
date: "2022-08-18"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(SimDesign)
library(rstan)
library(tidyverse)
library(gfoRmula)
expit<-function(x){1/(1+exp(-x))}
logit<-function(p){log(p)-log(1-p)}
```

## Notes on simulation:
- can add non-linearity in treatment assignment model
- autorunjags runs chain until converges
- 50000 iterations

## Log-likelihood function
```{r, echo = FALSE}
loglik2<-function(param,resp,mmat, weight){

  n<-length(resp)
  ### NOTE: param will have 5 entries, one for each theta (intercept, visit 1 treatment effect, visit 2 treatment effect, visit 1-2 interaction effect) and sigma (response)
  theta <- param[1:4] 
  
  sigma <- param[5]  ## only 1 sigma because end of study outcome.

  e<- (resp - mmat%*%theta)
  
  logl <- NA

  if (sigma > 0){
    
    logl1<- -0.5*log(sigma^2) - ((e)^2)/(2*(sigma^2)) ## ONly 1 log-likelihood, first one is good
    
    logl<- sum(weight*logl1)
    
  }
  return(logl)
  
}

```

### JAGS model
```{r, echo = FALSE}
cat( " model {

     #N = nobs
     for (i in 1:N) {

     # conditional treatment assignment model;
     
     logit(p1[i]) <- b10 + b11*x1[i] + b12*y1[i]
     z1[i] ~ dbern(p1[i])

     z2[i] ~ dbern(p2[i])
     logit(p2[i]) <- b20 + b21*x2[i] + b22*y2[i] + b23*z1[i]

     # marginal treatment assignment model;

     z1s[i] ~ dbern(p1s[i])
     logit(p1s[i]) <- bs10

     z2s[i] ~ dbern(p2s[i])
     logit(p2s[i]) <- bs20 + bs21*z1[i]
     }

     # Priors
     b10 ~ dunif(-5,5) #true 0;
     b11 ~ dunif(-5,5) #true 0.2;
     b12 ~ dunif(-5,5) #true -0.05;

     b20 ~ dunif(-5,5)
     b21 ~ dunif(-5,5)
     b22 ~ dunif(-5,5)
     b23 ~ dunif(-5,5) #true 2

     bs10 ~ dunif(-5,5)
     bs20 ~ dunif(-5,5)
     bs21 ~ dunif(-5,5)

     }",
         file = "model_unif.txt")


```

```{r, echo = FALSE}

mysim <- function(from=1, to=1, ntot=500, ncov=5, mean_x1=0.5, mean_x2=0.8, mean_x3=7, mean_x4=-0.9, mean_x5=1.5, mean_y=30, sigma_x1 = 1.2, sigma_x2 = 0.8, sigma_x3=0.9, sigma_x4=1.8, sigma_x5=0.2, sigma_y = 4,
  rho13 = -0.5, rho23 = 0.5, rho12 = 0.1, coeffz_x1 = 0.2, coeffz_x2 = 0.1, coeffz_y = -0.05, coeffz_z = 2,   rho12 = -0.5, rho13 = 0.5, rho14 = 0.9, rho15=-0.8,
  rho23 = 0.1, rho24 = -0.1, rho25 = 0.5,
  rho34 = 0.05, rho35 = -0.1,
  rho45 = -0.05,
    coeffz_x1 = 0.2, coeffz_x2 = 0.04, coeffz_x3 = 0.2, coeffz_x4 = 0.5, coeffz_x5 = 0.1, coeffz_y = -0.05, coeffz_z = 2,
  coeffx1_z = -0.3, coeffx2_z = 0.9, coeffx3_z = 0.3, coeffx4_z = 1.9, coeffx5_z = 0.1,
  trt_int = -.03,
    coeffy_x1 = 0.4, coeffy_x2 = -1.2, coeffy_x3 = -0.9, coeffy_x4 = 3, coeffy_x5 = 0.9,
  nobs = 100,
  alpha = 0.8,
  effect = 0.6,
  effect_int=-0.3,
  niter=15000, nburnin=5000, thin=5, nboot=2000) {
  
  i = 1;
  # Range of Number of simulation runs - lower bound
  from=1;
  # Range of Number of simulation runs - upper bound
  to=1;
  # Sample size
  ntot=500;
  # Number of covariates
  ncov=5;
  # Mean of X's and Y
  mean_x1=0.5; mean_x2=0.8; mean_x3=7; mean_x4=-0.9; mean_x5=1.5; 
  # Standard deviances of X's and Y
  # sigma_x1 = 1.2; sigma_x2 = 0.8; sigma_x3=0.9; sigma_x4=1.8; sigma_x5=0.2; sigma_y = 0.7;
  
  # for simplicity change all sigma to 1;
  sigma_x1 = 1; sigma_x2 = 1; sigma_x3=1; sigma_x4=1; sigma_x5=1; sigma_y = 1;

  # Correlation coefficients between pairwise X's
  rho12 = -0.5; rho13 = 0.5; rho14 = 0.5; rho15=-0.5;
  rho23 = -0.5; rho24 = -0.5; rho25 = 0.5;
  rho34 = 0.5; rho35 = -0.5;
  rho45 = -0.5;

  # Treatment assignment model coefficients
  coeffz_x1 = 0.2; coeffz_x2 = 0.04; coeffz_x3 = 0.2; coeffz_x4 = 0.5; coeffz_x5 = 0.1; coeffz_y = -0.05; coeffz_z = 2;

  # Treatment effects on X's
  coeffx1_z = -0.3; coeffx2_z = 0.9; coeffx3_z = 0.3; coeffx4_z = 1.9; coeffx5_z = 0.1;

  # Treatment effect interaction between visit 1 and 2, on X's
  trt_int = -.03

  # Covariate effects on Y ### CHANGE NOTATION SO THAT DEPENDENT VARIABLE IS ON LEFT
  coeffy_x1 = 0.4; coeffy_x2 = -1.2; coeffy_x3 = -0.9; coeffy_x4 = 3; coeffy_x5 = 0.9;
  coeffy_x = matrix(c(coeffy_x1, coeffy_x2, coeffy_x3, coeffy_x4, coeffy_x5), ncov, 1);

  # Empty y
  y =array(NA, c(2, 2, ntot));

  # Number of observations
  nobs = 100;

  # Number of discrete variables
  ncov_d=2;

  # Intercept effect on Y
  alpha = 0.8;

  # Treatment effect on Y at visit 1
  effect = 0.6;
  # Interaction effect between treatments at visit 1 and 2
  effect_int=-0.3

  #
  niter=15000; nburnin=5000; thin=5; nboot=2000;

  coeffy_x = matrix(c(coeffy_x1, coeffy_x2, coeffy_x3, coeffy_x4, coeffy_x5), ncov, 1)
  y =array(NA, c(2, 2, ntot))
  samplesize <- (niter - nburnin)/thin
  results <- matrix(NA, to, 26)
  
  ## Number of variables to keep track of, double-counting discrete variables as they will be generated using a continuous counterpart.
  nL <-ncov + ncov_d
  
  
  for (i in from:to) {
    
    ## Setting different seed for each simulation run
    iter <- 66500 + (i - 1)
    set.seed(iter)
    
    ## Matrix tracking all covariate values for all 3 visits, under each of the 2 Potential Outcomes for the first 2 visits. 
     #first dimension is 2; represents z1 = 0 and z1 = 1; 
     #second dimension is 2; represents z2 = 0 and z2 = 1; 
     #third dimension is ntot; represents number of subjects; 
     #fourth dimension k*nL represent visits for x1-x5, and x1d and x2d (the discrete versions of x1 and x2), in this order;
    L <- array(NA, c(2, 2, ntot, 2 * (nL))) 
   
    ## Matrix storing "observed" covariate values, so there is only 1 Potential Outcome per visit.
    Lobs <- matrix(NA, ntot, 2 * (nL))
    
    ## Observed treatment assignment
    z <- matrix(NA, ntot, 2)
    
    
    ### 1. visit 1:
    
    ## cov matrix of x1,x2,x3,x4,x5 
    s <- matrix(c(sigma_x1^2, (rho12)*sigma_x1*sigma_x2, (rho13)*sigma_x1*sigma_x3, (rho14)*sigma_x4*sigma_x1, (rho15)*sigma_x5*sigma_x1,
                  (rho12)*sigma_x1*sigma_x2, sigma_x2^2, (rho23)*sigma_x3*sigma_x2, (rho24)*sigma_x4*sigma_x2, (rho25)*sigma_x5*sigma_x2,
                  (rho13)*sigma_x1*sigma_x3, (rho23)*sigma_x2*sigma_x3, sigma_x3^2, (rho34)*sigma_x4*sigma_x3, (rho35)*sigma_x5*sigma_x3,
                  (rho14)*sigma_x1*sigma_x4, (rho24)*sigma_x2*sigma_x4, (rho34)*sigma_x3*sigma_x4, sigma_x4^2, (rho45)*sigma_x5*sigma_x4,
                  (rho15)*sigma_x1*sigma_x5, (rho25)*sigma_x2*sigma_x5, (rho35)*sigma_x3*sigma_x5, (rho45)*sigma_x4*sigma_x5, sigma_x5^2), 5, 5) 
    #test; 
    # det(s)
    
    ## Generating continuous X's
    Lobs[,1:(nL-ncov_d)] <- L[1,1,,1:(nL-ncov_d)] <- L[1,2,,1:(nL-ncov_d)] <- L[2,1,,1:(nL-ncov_d)] <- L[2,2,,1:(nL-ncov_d)] <- rmvnorm(ntot, c(mean_x1, mean_x2, mean_x3, mean_x4, mean_x5), s)
    ## Determining discrete counterpart of X1,X2
    Lobs[,(nL-(ncov_d - 1)):nL] <- L[1,1,,(nL-(ncov_d - 1)):nL] <- L[1,2,,(nL-(ncov_d - 1)):nL] <- L[2,1,,(nL-(ncov_d - 1)):nL] <- L[2,2,,(nL-(ncov_d - 1)):nL] <- ifelse(expit(Lobs[,1:ncov_d]) < 0.5, 0, 1)
    ## Linear predictor of treatment assignment model
    m_z<- Lobs[,nL-(ncov_d-1)] * coeffz_x1 + Lobs[,nL] * coeffz_x2 + Lobs[,3] * coeffz_x3 + Lobs[,4] * coeffz_x4 + Lobs[,5] * coeffz_x5
    ## Treatment assignment probability
    pz <- expit(m_z)
    ## Observed treatment assignment
    z[,1] <- rbinom(ntot,1,prob=pz)
    
    
    ### 2. visit 2:
    # for Z1 = 0;
    
    ## Generating continuous X's
    L[1,1,,(nL+1):(2*nL-ncov_d)] <- L[1,2,,(nL+1):(2*nL-ncov_d)] <- t(apply(L[1,1,,1:(nL-ncov_d)], 1, function(x){rmvnorm(1, mean = x, s)}))

    # for z1 = 1;

    ## Treatment effects on covariates
    trt<- matrix(c(rep(coeffx1_z,ntot), rep(coeffx2_z,ntot), rep(coeffx3_z,ntot), rep(coeffx4_z,ntot), rep(coeffx5_z,ntot)),ntot,ncov)
    
    ## Generating continuous X's
    L[2,1,,(nL+1):(2*nL-ncov_d)] <- L[2,2,,(nL+1):(2*nL-ncov_d)] <- t(apply( (L[2,1,,1:(nL-ncov_d)]) + trt, 1, function(x){rmvnorm(1, mean = x, s)})) 
    
    ## Determining discrete counterpart of X1,X2
    L[,,,((nL-(ncov_d-1)):nL)] <- ifelse(expit(L[,,,1:ncov_d]) < 0.5, 0, 1)
    L[,,,(2*nL-(ncov_d-1)):(2*nL)] <- ifelse(expit(L[,,,(nL+1):(nL+ncov_d)]) < 0.5, 0, 1)

    ## Extracting only the observed covariate values (based on observed treatment assignment)
    for (j in (nL+1):(2*nL)) {
      Lobs[,j] <- L[cbind(z[,1]+1,1,1:ntot,j)]
    }
    
    ## Linear predictor of treatment assignment model
    m_z<- Lobs[,2*nL-(ncov_d-1)] * coeffz_x1 + Lobs[,2*nL] * coeffz_x2 + Lobs[,3] * coeffz_x3 + Lobs[,4] * coeffz_x4 + Lobs[,5] * coeffz_x5 + coeffz_z*z[,1]
    ## Treatment assignment probability
    pz <- expit(m_z)
    ## Observed treatment assignment
    z[,2] <- rbinom(ntot,1,prob=pz)
    
    
    ## Cumulative treatments
    zobs <- rowSums(z)
    table(zobs)
    
    ## Observe outcomes
    lp <- alpha + effect*z[,1] + (effect**2)*z[,2] + effect_int*z[,1]*z[,2] + cbind(Lobs[,(2*nL-ncov_d + 1):(2*nL)] , Lobs[, (2*nL-ncov + 1):(2*nL-ncov_d)]) %*% coeffy_x
    yobs <- rnorm(n = nrow(Lobs), mean = lp, sd = sigma_y)
    

    # Kuan : old code to get the true y and true causal effect; Outcomes
      ylong <- NULL
      zlong <- NULL
      x2long <- NULL
      counter <- 1
      for (j in 0:1) {
          for (k in 0:1) {
                  ## Response model linear predictor
                  lp <- alpha + effect*j + (effect**2)*k + effect_int*j*k + cbind(L[j+1, k+1,,(2*nL-ncov_d + 1):(2*nL)] , L[j+1, k+1, ,(2*nL-ncov + 1):(2*nL-ncov_d)]) %*% coeffy_x    ## Should these covariates be used?
                  if(any(is.na(lp))){
                    L_na <- L[j+1,k+1,,(nL+1+ncov_d):(2*nL)]
                    lp_na <- lp
                    print(j)
                    print(k)
                  }
                  ## Applying link function (identity link) to get response values
                  y[j+1,k+1,] <- lp

                  ## Changing response values to long format
                  ylong <- c(ylong, y[cbind(j+1,k+1,1:ntot)])
                  
                  ## Changing treatment values to long format
                  zlong <- c(zlong, rep(j+k, ntot))
                  
                  ## Changing covariates at last visit to long format
                  x2long <- x2long %>% bind_rows(cbind(L[j+1, k+1,,(2*nL-ncov_d + 1):(2*nL)] , L[j+1, k+1, ,(2*nL-ncov + 1):(2*nL-ncov_d)]) %>% as.data.frame() %>% mutate(z1 = j, z2 = k))
              }
      }

    ## Extracting observed response values
    summary(ylong)
    summary(yobs)

    ## Potential treatment values for visits 1 and 2, respectively, in long format
    z1long <- c(rep(0, ntot*2), rep(1, ntot*2))
    z2long <- c(rep(0, ntot), rep(1, ntot), rep(0, ntot), rep(1, ntot))

    ## True Model
    truemodel <- lm(ylong ~ z1long*z2long + as.matrix(x2long[,1:5])) #in analysis, can investigate an incorrect likelihood where z1 and z2 have same effect
    summary(truemodel)

    ## True model results
    # mean of Y_00 and Y_11;
    y_00<-mean(predict(truemodel, newdata = cbind(z1long = 0, z2long=0, (x2long[,1:5]))))
    y_11<-mean(predict(truemodel, newdata = cbind(z1long = 1, z2long=1, (x2long[,1:5]))))
    results[i,1] <- y_11 - y_00 ## had error with i so subtracted 1
    #### GIVES SAME RESULT AS ADDING TREATMENT EFFECTS FROM TRUEMODEL
    results[i,2] <- vcov(truemodel)[2,2] ## had error with i so subtracted 1

      
    #creating observed wide datasets;
    obs<-data.frame(Lobs,z, z[,1], rowSums(z[,1:2]),rep(1,ntot),rep(2,ntot), yobs)
    colnames(obs) <- c(paste0("x1", 1:ncov), paste0("x1", 1:ncov_d, "d"), paste0("x2", 1:ncov), paste0("x2", 1:ncov_d, "d"),"z1", "z2","cumz1","cumz2", "visit1","visit2", "y")
    
    obs$id<-seq(1, ntot, by=1)
    #Creating observed long datasets to model weighted GEE (Kuan: update the creation of long data to incorporate the new observed y);
    lobs<-rbind( cbind(seq(1, ntot, by=1),Lobs[,1:nL],z[,1]),cbind(seq(1, ntot, by=1), Lobs[,(nL+1):(2*nL)],z[,2]))
    time<-c(rep(1, ntot), rep(2, ntot))
    lcumz<-c(z[,1], rowSums(z[,1:2]))
    obslong<-data.frame(lobs, time, lcumz)
    colnames(obslong)<-c("id", "x1", "x2", "x3", "x4", "x5", "x1d", "x2d", "z", "time", "lcumz")
    yobs_df <- data.frame(id = 1:ntot, y = yobs)
    obslong <- obslong %>% left_join(yobs_df, by = "id")
    obslong$y <- with(obslong, ifelse(time < 2, NA, y))
    # head(obslong)
    # dim(obslong) #1500 rows, 6 cols
    obslong <- obslong[order(obslong$id),] 
    # obslong$z_path <- with(obslong, ifelse(time < 2, NA, ifelse(lcumz == 2, "11", ifelse(lcumz==1 & z == 0, "10", ifelse(lcumz==1 & z == 1, "01", ifelse(lcumz == 0, "00", NA))))))
    # obslong$z1 <- with(obslong, ifelse(z_path %in% c("10", "11"), 1, 0))
    # obslong$z2 <- with(obslong, ifelse(z_path %in% c("01", "11"), 1, 0))
    # obslong$y_pred <- with(obslong, ifelse(time < 2, NA, alpha + effect*z1 + (effect**2)*z2 + effect_int*z1*z2 + as.matrix(cbind(x1d, x2d, x3, x4, x5)) %*% coeffy_x))


     # lm(y~ z1 * z2 + x1d + x2d + x3 + x4 + x5, data = obslong %>% filter(time == 2) ) %>% coef %>% round(., 5)

```

## Stan modelling
```{r, echo = FALSE}
stan_data <- list(N = nrow(Lobs),
                       N_cov = ncov,
                       x1 = Lobs[,(ncov_d+1):(ncov_d+ncov)],
                       x2 = Lobs[,(ncov+2*ncov_d+1):(2*ncov+2*ncov_d)],
                       z1 = z[,1],
                       z2 = z[,2],
                       z1_s = z[,1],
                       z2_s = z[,2])

```

```{r, include = FALSE}
mod <- stan(data = stan_data,
             file = ("JAGS model in stan.stan"),
             iter = 6000,
             seed = 243)
# summary(mod)[["summary"]]
print("done")

```

```{r, echo = FALSE}
mod_weight_numerator <- rstan::extract(mod)[[c("weight_numerator")]] %>% as.data.frame()

mod_weight_denominator <- rstan::extract(mod)[[c("weight_denominator")]] %>% as.data.frame()

weights_ratio <- colSums(mod_weight_numerator)/colSums(mod_weight_denominator)
print(1)

# wmean_s <- c(rep(1, ntot), weights_ratio)
wmean_s <- c(weights_ratio)

```

```{r, echo = FALSE}
# library(bayesplot)
# 
# set.seed(1856)
# z1 <- z[,1]
# z2 <- z[,2]
# z1rep1 <- rstan::extract(mod)[["z1_pred"]]
# z2rep1 <- rstan::extract(mod)[["z2_pred"]]
# ppc_dens_overlay(z1, z1rep1) 
# 
# mod_extract <- rstan::extract(mod)
# samp100 <- sample(nrow(yrep1), 100)
```

```{r, echo = FALSE}
## Gelman-Reuben index
## correlation plot - should not be correlated
# pars <- c("beta1")
# traceplot(mod, pars = pars)

## mcmc_pairs
##autorun jags (runs chain until convergence)
library(bayesplot)
library(rstanarm)
mod_summary <- summary(mod)
pairs(mod, pars = c("alpha1", "beta1"))

```

```{r, echo = FALSE}

    
    ## End of Study Outcome
    ## Widen such that each row is a patient. In wide form, previous y's y1 and y2 should be covariates because they're confounders
    ### Wide df: 6 columns for the two covariates x 3 visits, and 2 columns for treatments x2 visits and 1 column for cumz (z1 +), 3 columns for y (y1, y2, y).
    ### lm(y ~ cumz)
    truelong_endofstudy <- truelong %>% filter(time == 3)
    trueGEE_endofstudy <- geese(truelong$y~truelong$lcumz, id = truelong$id, data = truelong, family = gaussian, corstr = "ar1")
    coef(trueGEE_endofstudy)
    truelong_endofstudy %>% group_by(id)
    mean(coef(lm(y~lcumz+as.factor(id), data = truelong_endofstudy))[2:500])
    lm(data = truelong_endofstudy %>% group_by(id, lcumz) %>% summarise(y = mean(y)))
    # E(y11) - E(y00) this is saying E(Y01) is not the same as E(Y10)
    # lm(Y_endofstudy ~ cumz), cumz will be a ordinal variable 0,1,2
    
    # trueGEE2<-geese(truelong$y~truelong$lcumz+truelong$time, id = truelong$id, data = truelong, family = gaussian,corstr = "independence")
    # # summary(trueGEE2)
    # results[i,3] <- coef(trueGEE2)[2]
    # results[i,4] <- trueGEE2$vbeta[2,2]
    
    
    #unweighted GEE biased - naive approach;
    # "independence", "exchangeable", "ar1","unstructured" and "userdefined";
    # simpleGEE2<-geese(obslong$y~obslong$lcumz+obslong$time, id = obslong$id, data = obslong, family = gaussian, corstr = "ar1")
    # # summary(simpleGEE)
    # results[i,1] <- coef(simpleGEE2)[2]
    # results[i,2] <- simpleGEE2$vbeta[2,2]
    
    bootest3<-numeric(nboot)

    for (j8 in 1:nboot) {
      alpha <- as.numeric(rdirichlet(1, rep(1.0, ntot)))
       inits2 <- c(30,5,0.2,4,6)
      ## y_end ~ normal distribution with mean and sigma_squared. Mean is modelled by theta0+theta1*z1+theta2*z2 (if there's interaction, then add theta3*z1*z2). sigma has to be > 0. 0 for theta's and 1 for sigma as initial points. need design matrix
      maxim <- optim(inits2, fn=loglik2,resp=yobs, mmat=cbind(1, z[,1], z[,2], z[,1] * z[,2]), 
                     # mmat2=cbind(1,obs$cumz2,2),mmat3=cbind(1,obs$cumz3,3),
                     weight=alpha*wmean_s,
                     # control=list(fnscale=-1), method='BFGS', hessian=F)
                     control=list(fnscale=-1), method = "Nelder-Mead", hessian=F)
      bootest3[j8] <- maxim$par[2]


      if (j8 %% 50 == 0) {
        print(j8)
      }
    }
    

  }
  
}

```
## To-Do

Get True ATE 
Shorten to 2 visits (once g-computation matches with true model, can extend to 3 visits)
Compare true value to BMSM
Work on implementing TMLE

## G-Computation
### Dataset should be long: each row is a unique id-visit combination
### y is NA when visit isn't 2
### y in example code is binary
### what are w1, w2?
```{r, echo = FALSE}
obslong_new <- obslong %>% select(id, x1d, x2d, x3, x4, x5, time, z, y)
obslong_new$visit <- obslong_new$time
obslong_new$time <- obslong_new$visit - 1

    id <- 'id'
    time_name <- 'time'
    # create one to for the package
    covnames <- c("x1d", "x2d", "x3", "x4", "x5", "z")
    outcome_name <- 'y'
    covtypes <- c('binary', 'binary', 'normal', 'normal', 'normal', 'binary')
    histories <- c(lagged) ## Not sure what this is doing
    histvars <- list(c('z', "x1d", "x2d", "x3", "x4", "x5"))
    
    covparams <- list(covmodels = c(x1d ~ lag1_x1d + lag1_x2d + lag1_x3 + lag1_x4 + lag1_x5 + lag1_z ,
                                    x2d ~ lag1_x1d + lag1_x2d + lag1_x3 + lag1_x4 + lag1_x5 + lag1_z ,
                                    x3 ~ lag1_x1d + lag1_x2d + lag1_x3 + lag1_x4 + lag1_x5 + lag1_z ,
                                    x4 ~ lag1_x1d + lag1_x2d + lag1_x3 + lag1_x4 + lag1_x5 + lag1_z ,
                                    x5 ~ lag1_x1d + lag1_x2d + lag1_x3 + lag1_x4 + lag1_x5 + lag1_z ,
                                    z ~ x1d + x2d  + x3  + x4  + x5 + lag1_z))
    
    ymodel <- y ~ lag1_z + z + lag1_z*z + x1d + x2d  + x3  + x4  + x5
    
    intvars <- list('z', 'z')
    interventions <- list(list(c(static, rep(0, 2))),
                          list(c(static, rep(1, 2))))
    int_descript <- c('Never treat', 'Always treat')
    
    gform_cont_eof2 <- gformula_continuous_eof(
      obs_data = obslong_new,
      id = id,
      time_name = time_name,
      covnames =covnames,
      outcome_name = outcome_name, 
      covtypes = covtypes,
      covparams = covparams,  ymodel = ymodel,
      intvars = intvars, interventions = interventions,
      int_descript = int_descript, 
      ref_int = 1,
      histories = c(lagged), histvars = histvars,
      # basecovs = c("w1","w2"), 
      # boot_diag = TRUE,
      nsimul = 1000,
      nsamples = 1000, parallel = TRUE, ncores = 4,
      seed = 123)
    gform_cont_eof2
```


### SIMPLE SIMULATION CODE
```{r, echo = FALSE}
set.seed(1999)
ntot <- 1000
x_1 <- rnorm(ntot, mean = 0.4, sd = 0.1)
z_1 <- rbinom(ntot, 1, prob = expit(x_1))
x_2 <- rnorm(ntot, mean = x_1 + z_1*0.2)
z_2 <- rbinom(ntot, 1, prob = expit(x_2))
y <- z_2*0.60 + z_1 * 0.36 + z_1*z_2*(-0.3) + x_2*0.3 + 2 ## TRUE EFFECT IS 0.66
yobs <- rnorm(ntot, mean = y, sd = 0.4)
obslong2 <- data.frame(x = c(x_1, x_2), z = c(z_1, z_2), y = c(rep(NA, ntot), y))
obslong2$time <- c(rep(0, ntot), rep(1, ntot))
obslong2$id <- c(1:(ntot), 1:(ntot))

## WIDENING DATASET TO MAKE SURE DIFFERENT TREATMENT COMBINATIONS RESULT IN DIFFERENT Y VALUES
# obswide <- obslong2 %>% pivot_wider(names_from = time, values_from = c(x, y, z))
# obswide %>% group_by(z_0, z_1) %>% summarise(n(), mean(y_1))


    id <- 'id'
    time_name <- 'time'
    # create one to for the package
    covnames <- c("x", "z")
    outcome_name <- 'y'
    covtypes <- c('normal', 'binary')
    histories <- c(lagged) ## Not sure what this is doing
    histvars <- list(c('x', 'z'))
    
    covparams <- list(covmodels = c(x ~ lag1_x +  lag1_z,
                                    z ~ x + lag1_z))
    
    ymodel <- y ~ z + lag1_z + lag1_z*z + x
    
    intvars <- list('z', 'z')
    interventions <- list(list(c(static, rep(0, 2))),
                          list(c(static, rep(0, 2))))
    int_descript <- c('Never treat', 'Always treat')
    
    gform_cont_eof2 <- gformula_continuous_eof(
      obs_data = obslong2,
      id = id,
      time_name = time_name,
      covnames =covnames,
      outcome_name = outcome_name, 
      covtypes = covtypes,
      covparams = covparams,  ymodel = ymodel,
      intvars = intvars, interventions = interventions,
      int_descript = int_descript, 
      ref_int = 1,
      histories = c(lagged), histvars = histvars,
      # basecovs = c("w1","w2"), 
      # boot_diag = TRUE,
      nsimul = 1000,
      nsamples = 1000, parallel = TRUE, ncores = 4,
      seed = 123)
    gform_cont_eof2
```
